---
title: "Community"
output:
  html_document:
    toc: false
    toc_float: false
---
Teams from anywhere in the world are invited to submit forecasts once a week for one or more of the countries. Take a look at the [submission instructions](https://github.com/epiforecasts/covid19-forecast-hub-europe/wiki) and [get in touch](contact.html) with any questions.

# Teams

```{r teams, echo = FALSE, warning = FALSE, message = FALSE}
library("yaml")
library("purrr")
library("fs")
library("dplyr")

github_repo <- "epiforecasts/covid19-forecast-hub-europe"

team_df <-
  gh::gh(
    "/repos/{github_repo}/contents/{path}", 
    github_repo = github_repo, 
    path = "model-metadata"
  ) %>%
  map_chr("download_url") %>%
  set_names() %>%
  map(read_yaml) %>%
  imap_dfr(~ list(
    link = .y,
    authors = toString(purrr::map_chr(.x$model_contributors, "name")),
    model_abbr = .x$model_abbr,
    website_url = .x$website_url,
    team_name = .x$team_name,
    methods = .x$methods
  )) %>%
  mutate(
    md_link = glue::glue("[Metadata]({link})"),
    model_abbr = glue::glue("[{model_abbr}]({website_url})")
  ) %>%
  select(authors, model_abbr, team_name, md_link, methods) %>%
  arrange(tolower(model_abbr))

team_df  %>%
  relocate(
    "Model name" = model_abbr,
    "Authors" = authors,
    "Team" = team_name,
    "Methods" = methods,
    "Complete metadata" = md_link
  ) %>%
  knitr::kable(format = "markdown")
```

# The evaluation of the European Modelling Hubs

ECDC has conducted a survey among the participants of the European Modelling Hub, getting feedback and thus evaluating the European COVID-19 Forecast Hub, European COVID-19 Scenario Hub, and the European Modelling Hub meetings. The results and conclusions of the survey can be found below on the [European COVID-19 Scenario Hub webpage](https://covid19scenariohub.eu/about.html).


# Presentations

The ECDC hosts weekly calls which any forecasting team is welcome to join. Each week a different team is invited to present and discuss forecasting methods. Slides and extra content provided by the teams can be accessed below. Please note that slides might be released under a different license than the MIT license used for the rest of this website:

```{r presentations, results='asis', echo=FALSE}
files <- rev(fs::dir_ls("presentations"))

dates <- sub(
  "^([0-9]{4})-([0-9]{2})-([0-9]{2})-.*$",
  "\\3/\\2/\\1",
  basename(files)
)

nms <- files %>%
  fs::path_file() %>%
  fs::path_ext_remove() %>%
  substring(12) %>%
  { gsub("-", " ", .) }

sprintf(
  "- %s\t\t[%s](%s)",
  dates,
  nms,
  files
) %>%
  cat(sep = "\n")
```
