---
title: "Community"
output:
  html_document:
    toc: false
    toc_float: false
---
Teams from anywhere in the world are invited to submit forecasts once a week for one or more of the countries. Take a look at the [submission instructions](https://github.com/epiforecasts/covid19-forecast-hub-europe/wiki) and [get in touch](contact.html) with any questions.

# Teams

```{r teams, echo = FALSE, warning = FALSE, message = FALSE}
library("yaml")
library("purrr")
library("fs")
library("dplyr")

github_repo <- "epiforecasts/covid19-forecast-hub-europe"
branch <- "main"

team_df <-
  gh::gh(
        paste0("https://api.github.com/repos/{github_repo}/",
               "git/trees/{branch}?recursive=1"),
        github_repo = github_repo, branch = branch
        ) %>%
  pluck("tree") %>%
  keep(~ .x$type == "blob" &&
         grepl("metadata/", .x$path)) %>%
  map_chr(~ glue::glue(
                    paste0("https://raw.githubusercontent.com/{github_repo}/",
                           "{branch}/{.x$path}")
                  )) %>%
  set_names() %>%
  imap_dfr(~ c(link = .y, read_yaml(.x))) %>%
  select(link, model_abbr, team_name, website_url, methods) %>%
  mutate(
    md_link = glue::glue("[Metadata]({link})"),
    model_abbr = glue::glue("[{model_abbr}]({website_url})"),
    .keep = "unused"
  ) %>%
  arrange(tolower(model_abbr))

team_df  %>%
  relocate(
    "Model name" = model_abbr,
    "Affiliation" = team_name,
    "Methods" = methods,
    "Complete metadata" = md_link
  ) %>%
  knitr::kable(format = "markdown")
```

# Presentations

The ECDC hosts weekly calls which any forecasting team is welcome to join. Each week a different team is invited to present and discuss forecasting methods. Slides and extra content provided by the teams can be accessed below. Please note that slides might be released under a different license than the MIT license used for the rest of this website:

```{r presentations, results='asis', echo=FALSE}
library("httr")
url <- paste0("https://api.github.com/repos/epiforecasts/",
              "covid19-forecast-hub-europe-website/contents/presentations")
req <- GET(url)
stop_for_status(req)
files <- unlist(lapply(content(req), "[[", "name"))

for (file in rev(files)) {
  date <- sub("^([0-9]{4})-([0-9]{2})-([0-9]{2})-.*$", "\\3/\\2/\\1", file)
  name <- gsub("-", " ",
               sub("^[0-9]{4}-[0-9]{2}-[0-9]{2}-([^.]*)\\..*$", "\\1", file))
  url <-
    paste0("https://github.com/epiforecasts/",
           "covid19-forecast-hub-europe-website/raw/main/presentations/",
           file)
  cat(date, "\t\t", paste0("[", name, "](", url, ")"), "\n\n")
}
```
