---
title: "Citations & re-uses"
output:
  html_document:
    toc: false
    toc_float: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
bibfile <- "papers.bib"
```

To cite the European Covid-19 Forecast Hub in project in publications, please use the following references:

_Methodology and evaluation_

> Sherratt, K., Gruson, H., Johnson, H., Niehus, R., Prasse, B., Sandman, F., ... & Funk, S. (2022). Predictive performance of multi-model ensemble forecasts of COVID-19 across European nations. _eLife_. DOI: https://doi.org/10.7554/eLife.81916

_Data_

> Katharine Sherratt, Hugo Gruson, Helen Johnson, Rene Niehus, Bastian
> Prasse, Frank Sandman, Jannik Deuschel, Daniel Wolffram, Sam Abbott,
> Alexander Ullrich, Graham Gibson, Evan L Ray, Nicholas G Reich, Daniel
> Sheldon, Yijin Wang, Nutcha Wattanachit, Lijing Wang, Jan Trnka,
> Guillaume Obozinski, … Sebastian Funk. (2022). European Covid-19
> Forecast Hub (v2022.10.20) \[Data set\]. Zenodo.
> <https://doi.org/10.5281/zenodo.7229300>


Please [get in touch](contact.html) if you know or published an article using
data from the European Covid-19 Forecast Hub or mentioning it as a public health
tool.

```{r, results='asis'}
library(magrittr)
b <- tools::bibstyle(
  "by_year", 
  fmtPrefix = function(paper) "-", 
  .init = TRUE, 
  sortKeys = function(refs) rank(purrr::map_chr(unclass(refs), "year"))
)

bibtex::read.bib(bibfile) %>%
  purrr::keep(~ attr(unclass(.x), "bibtype") %in% c("Article", "PhdThesis")) %>%
  sort(.bibstyle = "by_year", decreasing = TRUE) %>%
  format("html", .bibstyle = "by_year") %>%
  paste(collapse = "") %>%
  cat()
```

